CYO Project Report - Brazilian Ecommerce

### 2021-07-12 finalReport.Rmd
updated with target encoding for customer starte, seller state, seller id.

# so raw data
raw_data <- orders_dataset %>% 
  inner_join(order_items_dataset,by='order_id') %>%
  inner_join(sellers_dataset,by='seller_id') %>% 
  inner_join(customers_dataset,by='customer_id') %>%  
  inner_join(products_dataset,by='product_id') %>%
  mutate(order_purchase_timestamp=as.numeric(order_purchase_timestamp),
         product_id=as.factor(product_id), 
         seller_id=as.factor(seller_id),
         seller_zip_code_prefix=as.factor(seller_zip_code_prefix),
         customer_unique_id=as.factor(customer_unique_id),
         customer_zip_code_prefix=as.factor(customer_zip_code_prefix),
         product_category_name=as.factor(product_category_name)) %>%
  select(-customer_id,-order_status,-seller_city,-seller_state,-customer_city,-customer_state, -payment_approved_at,-order_id,-order_item_id,-product_id,-seller_zip_code_prefix,-customer_unique_id,-customer_zip_code_prefix)
#  select(-customer_id,-order_status,-seller_city,-seller_state,-customer_city,-customer_state, -payment_approved_at,-order_id, -order_item_id, -product_id,-seller_zip_code_prefix,-customer_unique_id,-customer_zip_code_prefix)
```

@@

```{r Apply Target encoding, echo = FALSE}
  train_subset_for_encoding <- train_subset[1:30000,]
  global_mean <- mean(train_subset_for_encoding$number_of_hours)

@@

weight_to_use <- mean(weight_to_use_per_partition)  
```

```{r Post regularization, echo=FALSE}

@@

@@

tuningControl=trainControl(method = "cv", number = 3, p = .8)
knn_fit <- train(number_of_hours~., scaled_train_subset, method='knn',tuneGrid=data.frame(k=c(20,27,34)),trControl=tuningControl)

@@

RMSE(predictions,(scaled_test_subset %>% pull(number_of_hours) ))
#192.8755 for k=27

@@

```{r rf model, echo = FALSE}
set.seed(seed=1,sample.kind = 'Rounding')
tuningControl=trainControl(method = "cv", number = 2, p = .8)
rf_fit <- train(number_of_hours~., train_subset, method='rf',tuneGrid = data.frame(mtry = seq(5, 50, 10)),trControl=tuningControl,ntree=250) # nodesize = 50,maxnodes=2000,ntree=200

@@

RMSE(predictions,(test_subset %>% pull(number_of_hours) ))
# 184.5549 for mtry 15. Technically there are total of 79 variables due to 73 product categories and 6 other predictors

>>>>

# so raw data
raw_data <- orders_dataset %>% 
  inner_join(order_items_dataset,by='order_id') %>%
  inner_join(sellers_dataset,by='seller_id') %>% 
  inner_join(customers_dataset,by='customer_id') %>%  
  inner_join(products_dataset,by='product_id') %>%
  mutate(order_purchase_timestamp=as.numeric(order_purchase_timestamp),
         product_id=as.factor(product_id), 
         seller_id=as.factor(seller_id),
         seller_zip_code_prefix=as.factor(seller_zip_code_prefix),
         customer_unique_id=as.factor(customer_unique_id),
         customer_zip_code_prefix=as.factor(customer_zip_code_prefix),
         product_category_name=as.factor(product_category_name)) %>%
  select(-customer_id,-order_status,-seller_city,-customer_city, -payment_approved_at,-order_id,-order_item_id,-product_id,-seller_zip_code_prefix,-customer_unique_id,-customer_zip_code_prefix)
#  select(-customer_id,-order_status,-seller_city,-seller_state,-customer_city,-customer_state, -payment_approved_at,-order_id, -order_item_id, -product_id,-seller_zip_code_prefix,-customer_unique_id,-customer_zip_code_prefix)
```

@@

==TODO note penalty data should be calculated again if train_subset is changed. Only trained data should be used for test, so that there is no data leak.

```{r Apply Target encoding for seller_id, echo = FALSE}
#TODO you may need to remove customer_state and seller_state from dataset train_subset_for_encoding before proceeding further.

  train_subset_for_encoding <- train_subset[1:30000,]
  global_mean <- mean(train_subset_for_encoding$number_of_hours)

@@

weight_to_use <- mean(weight_to_use_per_partition)  
# 3
```

```{r Post regularization for seller_id effect, echo=FALSE}

@@

```{r Apply Target encoding for customer_state, echo = FALSE}
  train_subset_for_encoding <- train_subset[1:40000,] %>% select(-seller_state)
  global_mean <- mean(train_subset_for_encoding$number_of_hours)

  weights <- seq(0,30,15)

  test_weight_set <- test_weight_set %>%
    #semi_join(train_weight_set,by='product_category_name') %>%
    semi_join(train_weight_set,by='customer_state')

  weight_rmses <- sapply(weights, function(weight) {
      customer_state_effects <- train_weight_set %>% 
        group_by(customer_state) %>% 
        summarise(mean=mean(number_of_hours),n=n()) %>%
        mutate(mean=(n*mean+weight*global_mean)/(n+weight)) %>% 
        select(-n) %>% rename()

      train_weight_set <- train_weight_set %>% left_join(customer_state_effects,by='customer_state') %>% rename(customer_state_effect=mean) %>% select(-customer_state) #-product_category_name

      test_weight_set <- test_weight_set %>% left_join(customer_state_effects,by='customer_state') %>% rename(customer_state_effect=mean) %>% select(-customer_state) # -product_category_name,

      tuningControl=trainControl(method = "cv", number = 2, p = .8)
      knn_fit_for_weight <- train(number_of_hours~., scaled_train_subset, method='knn',tuneGrid=data.frame(k=c(20,27,34)),trControl=tuningControl)

      print(knn_fit_for_weight)

weight_to_use <- mean(weight_to_use_per_partition) 
# 20
```

```{r Post regularization with consumer state effect, echo=FALSE}

# prepare consumer_state_effect based on regularisation weight we have identified
  global_mean <- mean(train_subset$number_of_hours)

customer_state_effects_list <- lapply(1:5, function(index) {
    train_weight_set <- train_subset[-test_weight_indices[,index],]

    customer_state_effects <- train_weight_set %>% 
      group_by(customer_state) %>%
      summarise(mean=mean(number_of_hours),n=n()) %>%
      mutate(mean=(n*mean+weight_to_use*global_mean)/(n+weight_to_use)) %>% 
      select(-n) %>% rename()

    customer_state_effects
  }
)

cse <- customer_state_effects_list[[1]]
for (index in 2:5) {
   cse <- cse %>% full_join(customer_state_effects_list[[index]],by='customer_state', suffix=c("1",index))
}

# whereever value is NA, we have used global mean
cse <- cse %>% mutate(across(-customer_state,~if_else(is.na(.x),global_mean,.x)))

# as different partitions may not have exactly same data set combined the results
customer_state_effects <- tibble(cse[,1], customer_state_effect=rowMeans(cse[,-1],na.rm = TRUE))

train_subset <- train_subset %>% left_join(customer_state_effects,by='customer_state') %>% select(-customer_state) %>% mutate(customer_state_effect=if_else(is.na(customer_state_effect),global_mean,customer_state_effect))

test_subset <- test_subset %>% left_join(customer_state_effects,by='customer_state') %>% select(-customer_state)
```

```{r Apply Target encoding for seller_state, echo = FALSE}
  train_subset_for_encoding <- train_subset[1:40000,] 
  global_mean <- mean(train_subset_for_encoding$number_of_hours)

  weights <- seq(0,30,15)

  test_weight_set <- test_weight_set %>%
    #semi_join(train_weight_set,by='product_category_name') %>%
    semi_join(train_weight_set,by='seller_state')

  weight_rmses <- sapply(weights, function(weight) {
      seller_state_effects <- train_weight_set %>% 
        group_by(seller_state) %>% 
        summarise(mean=mean(number_of_hours),n=n()) %>%
        mutate(mean=(n*mean+weight*global_mean)/(n+weight)) %>% 
        select(-n) %>% rename()

      train_weight_set <- train_weight_set %>% left_join(seller_state_effects,by='seller_state') %>% rename(seller_state_effect=mean) %>% select(-seller_state) #-product_category_name

      test_weight_set <- test_weight_set %>% left_join(seller_state_effects,by='seller_state') %>% rename(seller_state_effect=mean) %>% select(-seller_state) # -product_category_name,

      tuningControl=trainControl(method = "cv", number = 2, p = .8)
      knn_fit_for_weight <- train(number_of_hours~., scaled_train_subset, method='knn',tuneGrid=data.frame(k=c(20,27,34)),trControl=tuningControl)

      print(knn_fit_for_weight)

weight_to_use <- mean(weight_to_use_per_partition)  
# 15
```

```{r Post regularization with seller state effect, echo=FALSE}

# prepare consumer_state_effect based on regularisation weight we have identified
  global_mean <- mean(train_subset$number_of_hours)

  set.seed(1,sample.kind='Rounding')
  test_weight_indices <- createDataPartition(train_subset$number_of_hours,p=0.2,times=10,list=FALSE)

seller_state_effects_list <- lapply(1:10, function(index) {
    train_weight_set <- train_subset[-test_weight_indices[,index],]

    seller_state_effects <- train_weight_set %>% 
      group_by(seller_state) %>%
      summarise(mean=mean(number_of_hours),n=n()) %>%
      mutate(mean=(n*mean+weight_to_use*global_mean)/(n+weight_to_use)) %>% 
      select(-n) %>% rename()

    seller_state_effects
  }
)

sse <- seller_state_effects_list[[1]]
for (index in 2:10) {
   sse <- sse %>% full_join(seller_state_effects_list[[index]],by='seller_state', suffix=c("1",index))
}

# whereever value is NA, we have used global mean
sse <- sse %>% mutate(across(-seller_state,~if_else(is.na(.x),global_mean,.x)))

# as different partitions may not have exactly same data set combined the results
seller_state_effects <- tibble(sse[,1], seller_state_effect=rowMeans(sse[,-1],na.rm = TRUE))

train_subset <- train_subset %>% left_join(seller_state_effects,by='seller_state') %>% select(-seller_state) %>% mutate(seller_state_effect=if_else(is.na(seller_state_effect),global_mean,seller_state_effect))

test_subset <- test_subset %>% left_join(seller_state_effects,by='seller_state') %>% select(-seller_state)
```

@@

tuningControl=trainControl(method = "cv", number = 3, p = .8)
knn_fit <- train(number_of_hours~., scaled_train_subset, method='knn',tuneGrid=data.frame(k=c(27,34,41)),trControl=tuningControl)

@@

RMSE(predictions,(scaled_test_subset %>% pull(number_of_hours) ))
#190.243 for k=41. The seller_state is not of much help. it decrease RMSE by .14

@@

```{r rf model, echo = FALSE}
set.seed(seed=1,sample.kind = 'Rounding')
tuningControl=trainControl(method = "cv", number = 2, p = .8)
rf_fit <- train(number_of_hours~., train_subset, method='rf',tuneGrid = data.frame(mtry = seq(5, 50, 10)),trControl=tuningControl,ntree=250)
#rf_fit <- train(number_of_hours~., train_subset %>% select(-seller_state), method='rf',tuneGrid = data.frame(mtry = seq(5, 50, 10)),trControl=tuningControl,ntree=250) # nodesize = 50,maxnodes=2000,ntree=200

@@

RMSE(predictions,(test_subset %>% pull(number_of_hours) ))
# 181.8166 for mtry 15. Technically there are total of 82 variables due to 73 product categories and 9 other predictors. The seller_state is not of much help. it increases RMSE by .6. So we should consider ignoring it.
